\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{hyperref}
\hypersetup{colorlinks=true,linkcolor=black,urlcolor=blue}
\setlength{\parskip}{0.75em}
\setlength{\parindent}{0pt}

\begin{document}
\title{Religion Practice and Happiness: Preliminary Findings}
\author{Research Automation Team}
\date{Prepared: 2025-11-04T08:17:22Z}\maketitle

\textbf{Seed:} 20251016 (from \texttt{config/agent_config.yaml})\\
\textbf{Dataset:} \texttt{childhoodbalancedpublic_original.csv}\\
\textbf{Privacy guardrail:} suppress cells with $n < 10$ (not triggered in reported results).

\section{Abstract}
We examine links between biological sex, active religious practice, and adult happiness change using the Childhood Balanced Public Survey. In the absence of calibrated survey weights, analyses treat the data as a simple random sample (SRS) with Taylor-linearized standard errors. Non-male respondents report higher rates of active religious practice than male respondents. Respondents raised in very strict religious environments report larger gains in adult happiness relative to childhood.

\section{Data and Design Context}
Sponsor-delivered files currently lack calibrated weights, strata, and primary sampling unit identifiers as documented in \texttt{docs/survey_design.yaml}. All estimates therefore assume equal-probability sampling. Design metadata gaps and sponsor follow-up requests are summarized in \texttt{reports/design_metadata_brief.md} and \texttt{reports/sponsor_follow_up.md}.

\section{Methods}
\subsection{H1: Active Religion Practice by Biological Sex}
Outcome: indicator for actively practicing a religion (recode $\texttt{religion} > 0$).\\
Grouping variable: biological sex (\texttt{biomale}).\\
Estimand: difference in weighted proportions (male minus non-male).\\
Analysis command:
\begin{verbatim}
python scripts/analyze_h1_religion_by_biomale.py \
  --csv childhoodbalancedpublic_original.csv \
  --config config/agent_config.yaml \
  --design docs/survey_design.yaml \
  --out tables/h1_religion_by_biomale.csv \
  --diff-out tables/h1_religion_by_biomale_diff.csv \
  --manifest artifacts/h1_religion_by_biomale_manifest.json
\end{verbatim}
Privacy guardrail: suppress cells with $n < 10$ (not triggered).

\subsection{H2: Childhood Religious Strictness and Adult Happiness Change}
Outcome: self-reported change in happiness (\texttt{On average, I am happier as an adult than I was in childhood (h33e6gg)}).\\
Exposure: terciles of childhood religious strictness (\texttt{externalreligion}), partitioned deterministically (0 $|$ 1--2 $|$ 3--4).\\
Estimand: pairwise differences in mean happiness change between terciles with Bonferroni correction.\\
Analysis command:
\begin{verbatim}
python scripts/analyze_h2_religion_strictness_vs_happiness.py \
  --csv childhoodbalancedpublic_original.csv \
  --config config/agent_config.yaml \
  --design docs/survey_design.yaml \
  --out tables/h2_happiness_by_religion_strictness.csv \
  --diff-out tables/h2_happiness_by_religion_strictness_diff.csv \
  --manifest artifacts/h2_religion_strictness_vs_happiness_manifest.json
\end{verbatim}
Privacy guardrail: suppress cells with $n < 10$ (not triggered).

\section{Results}
\subsection{H1 Findings}
Not biologically male respondents: 34.50\% active practice (SE 0.62\%, 95\% CI [33.29\%, 35.71\%]; $n = 5{,}931$).\\
Biologically male respondents: 28.65\% active practice (SE 0.49\%, 95\% CI [27.69\%, 29.61\%]; $n = 8{,}512$).\\
Difference (male minus non-male): $-5.84$ percentage points (SE 0.79, 95\% CI [$-7.39$, $-4.30$]).\\
Interpretation: Non-male respondents maintain higher active religious engagement under the SRS assumption.

\subsection{H2 Findings}
Mean happiness change values:
\begin{itemize}
  \item Tercile 1 (\texttt{externalreligion = 0}, $n = 5{,}224$): 0.779 (SE 0.027).
  \item Tercile 2 (\texttt{externalreligion} in [1, 2], $n = 5{,}801$): 0.675 (SE 0.026).
  \item Tercile 3 (\texttt{externalreligion} in [3, 4], $n = 3{,}411$): 0.819 (SE 0.033).
\end{itemize}
Bonferroni-adjusted pairwise differences:
\begin{itemize}
  \item Tercile 2 $-$ Tercile 1: $-0.104$ (SE 0.037, 95\% CI [$-0.193$, $-0.015$]).
  \item Tercile 3 $-$ Tercile 2: $0.144$ (SE 0.042, 95\% CI [$0.043$, $0.244$]).
  \item Tercile 3 $-$ Tercile 1: $0.040$ (SE 0.043, 95\% CI [$-0.062$, $0.142$]).
\end{itemize}
Interpretation: Strict childhood religious environments correlate with higher adult happiness change, whereas moderate strictness lags the other terciles.

\section{Discussion and Next Steps}
Results depend on the temporary SRS assumption; revisit once sponsor supplies calibrated weights and replicate design metadata. Upcoming work will extend analyses to hypotheses H-003 through H-005, integrate robustness checks, and quantify potential weight-induced shifts using sensitivity simulations. Maintain feature parity between this LaTeX document and the Markdown manuscript in \texttt{reports/manuscript.md} before submission.

\section{Reproducibility and Data Governance}
All commands above rely on deterministic scripts and the shared seed 20251016. Source tables reside in \texttt{tables/h1_religion_by_biomale*.csv} and \texttt{tables/h2_happiness_by_religion_strictness*.csv} with manifests in \texttt{artifacts/}. Privacy policy: suppress estimates derived from fewer than 10 respondents; current tables meet this criterion.

\end{document}
